---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# GEARS

<!-- badges: start -->


<!-- badges: end -->

The goal of GEARS is to reconstruct Gaussian Bayesian network and compare two networks (identical or differential) with graph ordering unknown.

## Installation

You can install the released version of GEARS from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("GEARS")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("han16/GEARS")
```

In case people have installation problem, try this 

```
remove.packages(c("curl","httr"))
install.packages(c("curl", "httr"))
Sys.setenv(CURL_CA_BUNDLE="/usr/lib64/microsoft-r/3.4/lib64/R/lib/microsoft-r-cacert.pem")
devtools::install_git("https://github.com/han16/GEARS")

```
## Example


```{r example}
library(GEARS)
## basic example code
head(exampleData1)
head(exampleData4)

```
* `exampleData1` is the regression coefficient in the network
* `exampleData4` is one simulated data set with number of node as the number of the columns, 10. 


## Reference 

[Gaussian Bayesian network comparisons with graph ordering unknown](https://www.sciencedirect.com/science/article/abs/pii/S0167947320302474)
